---
title: "HW-1 Tejas Patil"
author: "Tejas Jayant Patil"
date: "22 January 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
```

Homework 1

PART A

Problem 1

```{r 1}

aa <- mpg
selectcols <- function(dataset,...){
  colargument=unlist(list(...))
  newsubset= (dataset[,colargument])
  return(newsubset)
}
columnname <- selectcols(mpg,'year','drv')

sample_n(columnname,5)
is.data.frame(columnname)

colnumber <- selectcols(mpg,1,2,10,11)
sample_n(colnumber,5)
is.data.frame(colnumber)


```



Problem 2

```{r 2}
mpg
plotcols <- function(Data){
  names <- names(Data)
  for(i in names ){
    if(is.numeric(Data[[i]])){
      print(ggplot(Data,aes_string(i))+geom_histogram())
      }
  else{
    print(ggplot(Data,aes_string(i))+geom_bar())
  }      
      
    }
}
plotcols(mpg)

```  


PART B



``` {r 3}
##PROBLEM 3

Diamondstat <- diamonds
plot1 <-ggplot(Diamondstat,aes(x=factor(color),y=price))
plot2 <- (plot1 + geom_boxplot(aes(fill=factor(color))))
plot3 <-plot2 + xlab('Diamond Color(Best ---> Worst)') +
        ylab('Diamond price in US Dollars') +ggtitle(' Diamond Color vs Price boxplot')
plot3 

```
As seen from the documentation the color codes gives us quality of the diamond, 
from D(Best) to J (Worst).

From the plot we can infer anything , as the we can see there are lot of outliers in each plot which doesn't gives us the sufficient information to infer something.

It does shows that there is great variation in the 
prices of same type of diamond type, but doesn't indicate the reason for this vairation. 

Therefore this  graph is not that helpful to study this dataframe.

```{r 4}
## PROBLEM 4

df<- diamonds
pl <-ggplot(df,aes(x=factor(color),y=carat))
pl2<- (pl + geom_boxplot(aes(fill=factor(color))))
pl3<-pl2 + xlab('Diamond Color  (Best ---> Worst)') +
     ylab('Weight of Diamond in Carat') + ggtitle(' Diamond Color vs Diamond Weight')
pl3

```

This graph is informative than the previous one.The outliers in this graph are less than the previous one.

This is somewhat a positive type of graph,values increasing as we go  along the x axis.

With this  graph we can say that the best qualities diamond are often in small carats.
The larger the carat size the more worst the quality of Diamonds.

Problem 5

```{r 5}
## PROBLEM 5

df <- diamonds
Scatterplot1<- ggplot(df,aes(x=carat,y=price))
Scatterplot2<- Scatterplot1 + geom_point(aes(color=factor(color)))
Scatterplot3<- Scatterplot2 + facet_grid(.~color)+ stat_smooth()
Scatterplot4<- Scatterplot3 + xlab('Weight of Diamonds in Carats') + 
      ylab('Price in US Dollars') + ggtitle('Comparison of Diamods (Best ---> Worst)')
Scatterplot4

```
This graph gives us very informative insights in the Diamondstat. By comparing the different grades of diamond(Color factor D to J) along with its weight and Price we can infer a lot through this Graph. 

All the Diamonds are available are same price range,the thing which factors them out is the Color grade and its weight.

As we see from the graphs,one can get a (worst / best) Quality of diamond at same price, compromising its weight. Price for Large Diamond,worst Quality ~  Price for Small Diamond,Best Quality.




Problem 5
```{r 5b}
##problem 5

df <- diamonds
scatter1 <-ggplot(df,aes(x=carat,y=price))
scatter2<- scatter1 + geom_point(aes(color=factor(color),size=2))+geom_smooth()
scatter3<- scatter2 + xlab('weight of Diamond')+ylab('Price in US Dollars')+ggtitle('weight of Diamond Vs price')
scatter3

```